%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Presentations}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvpresentations}

%------------------------------------------------

\cvpresentation
{\textbf{Wildman, A.}; Cruzeiro, V.W.D.; Paesani, F.; Li, X. Origins of X-Ray Emission 1b$_1$ Splitting in Liquid Water. European Summer School for Quantum Chemistry} % Presentation
{Palermo, IT} % Location
{Sept. 2019} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{Wildman, A.}; Dembowski, M.; Graham, T. R.; Martinez Baez, E.; Gorniak, R. M.; Pouvreau, M. J.; Prange, M.; Krzysko, A. J.; Zhang, X.; Semrouni, D.; Wang, H-W.; Li, X.; Schenter, G. K.; Rosso, K. M.; Pearce, C. I.; Clark, A. E.; Clark, S. B. Relating Struture to Spectroscopic Signatures. 2019 Energy Frontier Research Centers Principal Investigators' Meeting}
{Washington, D.C.} % Location
{Jul. 2019} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{Wildman, A.}; Paesani, F.; Li, X. Origins of Hydrogen-Bonding Driven X-Ray Emission Splitting in Liquid Water. Northwest Theoretical and Computational Chemistry Conference.} % Presentation
{Pullman, WA} % Location
{Jun. 2019} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{Wildman, A.}; Boland, N.E. Oxalic Acid Influences Kinetics of Strong Chelate Exchange Reactions. 251st American Chemical Society National Meeting and Exposition.} % Presentation
{San Diego, CA} % Location
{Mar. 2016} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{Wildman, A.}; Boland, N.E. Influence of Oxalic Acid on Rates of Ligand Exchange between Strong Chelating Agents. 24th Annual Murdock College Science Research Conference.} % Presentation
{Vancouver, WA} % Location
{Nov. 2015} % Date(s)

%------------------------------------------------

\end{cvpresentations}
\vspace{-1cm}
