%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvpublications}

%------------------------------------------------

\cvpublication
{15.} 
{\textbf{Wildman, A.}; Zhao, L.; Tao, Z.; Pavo\v{s}evi\'{c}, F.; Hammes-Schiffer, S.; Li, X. Solvated Nuclear-Electronic Orbital Structure and Dynamics. \textit{In Preparation}}

%------------------------------------------------

\cvpublication
{14.} 
{Cruzeiro, V.W.D.; \textbf{Wildman, A.}; Li, X.; Paesani, F. Relationship between Hydrogen-Bonding Motifs and the 1b$_1$ Splitting in the X-Ray Emission Spectrum of Liquid Water. \textit{The Journal of Physical Chemistry Letters}, 2021, 12. DOI: 10.1021/acs.jpclett.1c00486}

%------------------------------------------------

\cvpublication
{13.} 
{Shelby, M.L.; \textbf{Wildman, A.}; Hayes, D.; Mara, M.W.; Lestrange, P.J.; Cammarata, M.; Balducci, L.; Artamonov, M.; Lemke, H.T.; Zhu, D.; Seideman, T.; Hoffman, B.M.; Li, X.; Chen, L.X. Interplays of Electron and Nuclear Motions along CO Dissociation Trajector in Myoglobin Revealed by Ultrafast X-Rays and Quantum Dynamics Calculations. \textit{Proceedings of the National Academy of Sciences}, 2021, 118. DOI: 10.1073/pnas.2018966118}


%------------------------------------------------

\cvpublication
{12.} 
{Zhao, L.; \textbf{Wildman, A.}; Pavo\v{s}evi\'{c}, F.; Tully, J.C.; Hammes-Schiffer, S.; Li, X. Excited State Intramolecular Proton Transfer with Nuclear-Electronic Orbital Ehrenfest Dynamics \textit{The Journal of Physical Chemistry Letters}, 2021, 12. DOI: 10.1021/acs.jpclett.1c00564}


%------------------------------------------------

\cvpublication
{11.} 
{Grofe, A.; Zhao, R.; \textbf{Wildman, A.}; Stetina, T.F.; Li, X.; Bao, P.; Gao, J. Generalization of Block-Localized Wave Function for Constrained Optimization of Excited Determinants \textit{The Journal of Chemical Theory and Computation}, 2020, 17. DOI: 10.1021/acs.jctc.0c01049}


%------------------------------------------------

\cvpublication
{10.} 
{Zhao, L.; \textbf{Wildman, A.}; Tao, Z.; Schneider, P.; Hammes-Schiffer, S.; Li, X. Nuclear-Electronic Orbital Ehrenfest Dynamics \textit{The Journal of Chemical Physics}, 2020, 153. DOI: 10.1063/5.0031019}

%------------------------------------------------

\cvpublication
{9.} 
{Kuda-Singappulige, G.U.; \textbf{Wildman, A.}; Lingerfelt, D.B.; Li, X.; Aikens, C.M. Ultrafast Nonradiative Decay of a Dipolar Plasmon-like State in Napthalene \textit{The Journal of Physical Chemistry A}, 2020, 124. DOI: 10.1021/acs.jpca.0c09564}

%------------------------------------------------

\cvpublication
{8.} 
{Lu, L.*; \textbf{Wildman, A.}*; Jenkins, A.J.; Young, L.; Clark, A.E.; Li, X. The ``Hole'' Story in Ionized Water from the Perspective of Ehrenfest Dynamics. \textit{The Journal of Physical Chemistry Letters}, 2020, 11. DOI: 10.1021/acs.jpclett.0c02987}

%------------------------------------------------

\cvpublication
{7.} 
{Zhao, L.; Tao, Z.; Pavo\v{s}evi\'{c}, F.; \textbf{Wildman, A.}; Hammes-Schiffer, S.; Li, X. Real-Time Time-Dependent Nuclear-Electronic Orbital Approach: Dynamics beyond the Born-Oppenheimer Approximation. \textit{The Journal of Physical Chemistry Letters}, 2020, 11. DOI: 10.1021/acs.jpclett.0c00701}

%------------------------------------------------

\cvpublication
{6.} 
{Williams-Young, D. B.; Petrone, A.; Sun, S.; Stetina, T. F.; Lestrange, P.;
Hoyer,  C. E.;  Nascimento, D. R.; Koulias, L. ; \textbf{Wildman, A.}; Kasper, J. M.; 
Goings, J. J.; Ding, F. ; DePrince III, A. E.; Valeev, E. F.; Li, X. The Chronus
Quantum (ChronusQ) Software Package. \textit{WIREs Comput. Mol. Sci}, 2019, 10. DOI: 10.1002/wcms.1436}

%------------------------------------------------

\cvpublication
{5.} 
{Clark, A. E.; Servis, M. J.; Liu, Z.; Martinez-Baez, E.; Su, J.; Batista, E.
R.; Yang, P.; \textbf{Wildman, A.}; Stetina, T.; Li, X.; Newcomb, K.; Maginn,
E. J.; Autschbach, J.; Dixon, D. A.  Solvent Extraction through the Lens of
Advanced Modeling and Simulation.  \textit{Ion Exchange and Solvent
Extraction}, 2019, 23, Chapter 5. DOI: 10.1201/9781315114378}
%------------------------------------------------

\cvpublication
{4.} 
{Liu, H.; Jenkins, A.J.; \textbf{Wildman, A.}; Frisch, M.J.; Lipparini, F.; Mennucci,
B.; Li, X. Time-Dependent Complete Active Space Embedded in a Polarizable Force
Field.  \textit{J. Chem. Theory Comput.}, 2019, 15. DOI:
10.1021/acs.jctc.8b01152} 

%------------------------------------------------

\cvpublication
{3.} 
{\textbf{Wildman, A.}; Donati, G.; Lipparini, F.; Mennucci, B.; Li, X.
Nonequilibrium Environment Dynamics in a Frequency-Dependent Polarizable
Embedding Model, \textit{J. Chem. Theory Comput.} 2018, 15. DOI:
10.1021/acs.jctc.8b00836} 

%------------------------------------------------

\cvpublication
{2.} 
{\textbf{Wildman, A.}; Martinez-Baez, E.; Clark, A.; Li, X. Anticorrelated
contributions to pre-edge features of aluminate near-edge X-ray absorption
spectroscopy in concentrated electrolytes, \textit{J. Phys. Chem. Lett.},
2018, 9. DOI: 10.1021/acs.jpclett.8b00642} 

%------------------------------------------------

\cvpublication
{1.}
{\parbox[t]{0.95\textwidth}{\strut Donati, G.*; \textbf{Wildman, A.}*; Caprasecca, S; Lingerfelt, D.B.; Lipparini,
F.; Mennucci, B.; Li, X., Coupling Real-Time Time Dependent Density Functional
Theory with Polarizable Force Field, \textit{J. Phys. Chem. Lett.}, 2017, 8.
DOI: 10.1021/acs.jpclett.7b02320. \\ \**\textbf{Co-First Authors}}}

%------------------------------------------------


\end{cvpublications}
\vspace{-1cm}

