%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Conferences/Talks}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvpresentations}

%------------------------------------------------

\cvpresentation
{\textbf{IDREAM EFRC Meeting}, Oral Presentation: 
Ultrafast Processes After Low-energy Electron Attachment in Water-Clusters: An \textit{ab initio} Study by Real-Time Nuclear-Electronic Orbital Density Functional Theory.
}
{PNNL, WA} % Location
{Oct. 2024} % Date(s)

\cvpresentation
{\textbf{ACS Spring 2024}, Oral Presentation: 
Multicomponent Cholesky Decomposition: Application to Nuclear–Electronic Orbital Theory.
} % Presentation
{New Orleans, LA} % Location
{Mar. 2024} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{EFRC-Hub-CMS-CCS PI Meeting}, Poster: 
Multiscale Nuclear-Electronic Orbital Quantum Dynamics in Complex Environments.
}
{Virtual} % Location
{Sept. 2023} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{EFRC-Hub-CMS-CCS PI Meeting}, Poster:
Radiolysis in Extreme Environments.
}
{Virtual}
{Sept. 2023} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{IDREAM EFRC Meeting}, Oral Presentation: 
A Computational Study of Potassium Potassium K-Edge XANES Spectra.
}
{PNNL, WA} % Location
{Aug. 2023} % Date(s)

%------------------------------------------------


\cvpresentation
{\textbf{SciDac Summit}, Oral Presentation: 
Simultaneous Optimization of Nuclear–Electronic Orbitals, 
SciDac Summit, 2022} % Presentation
{LBNL, CA} % Location
{Dec. 2022} % Date(s)

%------------------------------------------------

\cvpresentation
{\textbf{Vanderbilt Student Research Fair}, Oral Presentation: 
Structural Modeling and Validation of CNIH1 Protein. } % Presentation
{Nashville, TN} % Location
{Sept. 2019} % Date(s)


%------------------------------------------------

\end{cvpresentations}
\vspace{-1cm}
